RadLib: a radiative heat transfer model library for CFD

### 2021-01-01 submissions/initial_submission/manuscript.tex
renaming files, adding submission

Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces. The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry, making it a versatile tool for any simulation that requires radiative heat transfer, regardless of configuration. The interfaces, solver, and examples included with the library serve to illustrate its use and validate the implementation and results. 
%
\begin{figure}
	\begin{center}
		\includegraphics[width=\textwidth]{../figures/radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%

@@

Figure~\ref{f:examples} shows comparative results for the different radiation models for these cases. 
%
\begin{figure}
    \begin{center}
    \begin{tabular}{c c}
        Example S1 & Example S2 \\
        \includegraphics[width=2.75 in]{ex_1.pdf} &
        \includegraphics[width=2.75 in]{ex_2b.pdf} \\
        Example S3 & Example S4 \\
        \includegraphics[width=2.75 in]{ex_3a.pdf} &
        \includegraphics[width=2.75 in]{ex_4a.pdf} \\
        Example S5 & Example B3 \\
        \includegraphics[width=2.75 in]{ex_5b.pdf} &
        \includegraphics[width=2.75 in]{ex_6.pdf}
    \end{tabular}
    \caption{Results for examples summarized in Table~\ref{t:examples}.}
    \label{f:examples}
    \end{center}
\end{figure}
%
In general, the PM model performs poorly compared to the WSSGG and RCSLW models. A notable exception is Example S4. In Example S2, the PM $q(L)/\sigma T^4$ is off scale at an essentially constant at a value of unity. The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, giving optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively, which are relatively small compared to the isothermal domain size greater than 0.5 m. Example S5 omits the PM model to more clearly show the behavior of the WSGG and RCSLW models. For that example, the PM values follow the shape of the other curves but $Q$ varies from around -80 at $x=0$ to a peak of 200 at x=$1.5$ m, and dropping to 100 kW/m$^3$ at $x=2$ m. In all examples, four gray ($n=4$) and one clear gas are computed for the RCSLW models to give a consistent comparison to the WSGG model. Example S5 shows the sensitivity of the RCSLW model to the number of gases used. The difference between $n=2$ and $n=8$ is very small for all examples shwon, except for Example S2. When $n$ is increased from four to eight for that example the RCSLW model improves to show nearly perfect agreement with the LBL data.
In all Examples, the RCSLW model is initialized using the mean temperature and composition on the domain. In Example S5, the RCSLW model converges to the LBL solution when the model is initialized using the maximum temperature instead of the average temperature.

Figure~\ref{f:exSb1} shows the results from Example Sb1, which includes soot radiation. Results for three values of the soot volume fraction are shown. Both the WSGG and RCSLW models perform very well for each case. 
%
\begin{figure}
    \begin{center}
        \includegraphics[width=5.5 in]{ex_Sb1.pdf}
    \caption{Results for Example Sb1 summarized in Table~\ref{t:examples}.}
    \label{f:exSb1}
    \end{center}
\end{figure}
%

@@

\bibliographystyle{elsarticle-num} 
\bibliography{references}

>>>>

Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces. The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry, making it a versatile tool for any simulation that requires radiative heat transfer, regardless of configuration. The interfaces, solver, and examples included with the library serve to illustrate its use and validate the implementation and results. 
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%

@@

Figure~\ref{f:examples} shows comparative results for the different radiation models for these cases. 
%
\begin{figure}
    \begin{center}
    \begin{tabular}{c c}
        Example S1 & Example S2 \\
        \includegraphics[width=2.75 in]{fig_ex_1.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_2b.pdf} \\
        Example S3 & Example S4 \\
        \includegraphics[width=2.75 in]{fig_ex_3a.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_4a.pdf} \\
        Example S5 & Example B3 \\
        \includegraphics[width=2.75 in]{fig_ex_5b.pdf} &
        \includegraphics[width=2.75 in]{fig_ex_6.pdf}
    \end{tabular}
    \caption{Results for examples summarized in Table~\ref{t:examples}.}
    \label{f:examples}
    \end{center}
\end{figure}
%
In general, the PM model performs poorly compared to the WSSGG and RCSLW models. A notable exception is Example S4. In Example S2, the PM $q(L)/\sigma T^4$ is off scale at an essentially constant at a value of unity. The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, giving optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively, which are relatively small compared to the isothermal domain size greater than 0.5 m. Example S5 omits the PM model to more clearly show the behavior of the WSGG and RCSLW models. For that example, the PM values follow the shape of the other curves but $Q$ varies from around -80 at $x=0$ to a peak of 200 at x=$1.5$ m, and dropping to 100 kW/m$^3$ at $x=2$ m. In all examples, four gray ($n=4$) and one clear gas are computed for the RCSLW models to give a consistent comparison to the WSGG model. Example S5 shows the sensitivity of the RCSLW model to the number of gases used. The difference between $n=2$ and $n=8$ is very small for all examples shwon, except for Example S2. When $n$ is increased from four to eight for that example the RCSLW model improves to show nearly perfect agreement with the LBL data.
In all Examples, the RCSLW model is initialized using the mean temperature and composition on the domain. In Example S5, the RCSLW model converges to the LBL solution when the model is initialized using the maximum temperature instead of the average temperature.

Figure~\ref{f:exSb1} shows the results from Example Sb1, which includes soot radiation. Results for three values of the soot volume fraction are shown. Both the WSGG and RCSLW models perform very well for each case. 
%
\begin{figure}
    \begin{center}
        \includegraphics[width=5.5 in]{fig_ex_Sb1.pdf}
    \caption{Results for Example Sb1 summarized in Table~\ref{t:examples}.}
    \label{f:exSb1}
    \end{center}
\end{figure}
%

@@

%\bibliographystyle{elsarticle-num} 
%\bibliography{references}

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{Hottel_1967}
H.~Hottel, A.~Sarofim, Radiative Transfer, {McGraw-Hill}, New York, 1967.

\bibitem{Modest_2013}
M.~F. Modest, Radiative Heat Transfer, third edition Edition, {Academic Press},
  New York, 2013.

\bibitem{Smith_2003}
N.~Smith, J.~Gore, J.~Kim, Q.~Tang,
  \href{https://tnfworkshop.org/radiation/}{{TNF} workshop radiation models}
  (2003).
\newline\urlprefix\url{https://tnfworkshop.org/radiation/}

\bibitem{Grosshandler_1993}
W.~L. Grosshandler, {RADCAL}: A narrow-band model for radiation calculations in
  a combustion environment: Nist technical note 1402.

\bibitem{Barlow_2001}
R.~S. Barlow, A.~N. Karpetis, J.~H. Frank, J.-Y. Chen, Scalar profiles and {NO}
  formation in laminar opposed-flow partially premixed methane/air flames,
  Combustion and Flame 127~(3) (2001) 2102--2118.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00313-3}
  {\path{doi:10.1016/S0010-2180(01)00313-3}}.

\bibitem{Barlow_1999}
R.~Barlow, N.~Smith, J.~Chen, R.~Bilger,
  \href{http://www.sciencedirect.com/science/article/pii/S0010218098000716}{Nitric
  oxide formation in dilute hydrogen jet flames: isolation of the effects of
  radiation and turbulence-chemistry submodels}, Combustion and Flame 117~(1-2)
  (1999) 4--31.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(98)00071-6}
  {\path{doi:10.1016/S0010-2180(98)00071-6}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218098000716}

\bibitem{Frank_2000}
J.~H. Frank, R.~S. Barlow, C.~Lundquist, Radiation and nitric oxide formation
  in turbulent non-premixed jet flames, Proceedings of the Combustion Institute
  28~(1) (2000) 447--454.
\newblock \href {http://dx.doi.org/10.1016/S0082-0784(00)80242-8}
  {\path{doi:10.1016/S0082-0784(00)80242-8}}.

\bibitem{Zhu_2002}
X.~Zhu, J.~Gore, A.~N. Karpetis, R.~S. Barlow,
  \href{http://www.sciencedirect.com/science/article/pii/S0010218002003413}{The
  effects of self-absorption of radiation on an opposed flow partially premixed
  flame}, Combustion and Flame 129~(3) (2002) 342--345.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(02)00341-3}
  {\path{doi:10.1016/S0010-2180(02)00341-3}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218002003413}

\bibitem{Coelho_2002}
P.~J. Coelho, O.~J. Teerling, D.~Roekaerts, Spectral radiative effects and
  turbulence-radiation-interaction in sandia flame {D}, in: {Barlow, Robert S.,
  Pope, Stephan B., Masri, Assaad R., Oefelein, Joseph C.} (Ed.), The
  Proceedings of the Sixth International Workshop on Measurement and
  Computation of Turbulent Nonpremixed Flames, 2002.

\bibitem{Bordbar_2014}
M.~H. Bordbar, G.~Wecel, T.~Hyppanen, A line by line based weighted sum of gray
  gases model for inhomogeneous {CO$_2$–H$_2$O} mixture in oxy-fired
  combustion, Combustion and Flame 161~(9) (2014) 2435--2445.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2014.03.013}
  {\path{doi:10.1016/j.combustflame.2014.03.013}}.

\bibitem{Bordbar_2020}
H.~Bordbar, G.~C. Fraga, S.~Hostikka,
  \href{http://www.sciencedirect.com/science/article/pii/S0735193319302660}{An
  extended weighted-sum-of-gray-gases model to account for all {CO$_2$-H$_2$O}
  molar fraction ratios in thermal radiation}, International Communications in
  Heat and Mass Transfer 110 (2020) 104400.
\newblock \href {http://dx.doi.org/10.1016/j.icheatmasstransfer.2019.104400}
  {\path{doi:10.1016/j.icheatmasstransfer.2019.104400}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0735193319302660}

\bibitem{Rothman_2010}
L.~S. Rothman, I.~E. Gordon, R.~J. Barber, H.~Dothe, R.~R. Gamache, A.~Goldman,
  V.~I. Perevalov, S.~A. Tashkun, J.~Tennyson,
  \href{http://www.sciencedirect.com/science/article/pii/S002240731000169X}{{HITEMP},
  the high-temperature molecular spectroscopic database}, Journal of
  Quantitative Spectroscopy {\&} Radiative Transfer 111~(15) (2010) 2139--2150.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.05.001}
  {\path{doi:10.1016/j.jqsrt.2010.05.001}}.
\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S002240731000169X}

\bibitem{Solovjov_2016}
V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The generalized {SLW}
  model, Journal of Physics: Conference Series 676 (2016) 1--36.

\bibitem{Solovjov_2017}
V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The rank correlated
  {SLW} model of gas radiation in non-uniform media, Journal of Quantitative
  Spectroscopy {\&} Radiative Transfer 197 (2017) 26--44.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2017.01.034}
  {\path{doi:10.1016/j.jqsrt.2017.01.034}}.

\bibitem{Badger_2019}
J.~Badger, B.~W. Webb, V.~P. Solovjov, An exploration of advanced {SLW}
  modeling approaches in comprehensive combustion predictions, Combustion
  Science and Technology 012022~(676) (2019) 1--17.
\newblock \href {http://dx.doi.org/10.1080/00102202.2019.1678907}
  {\path{doi:10.1080/00102202.2019.1678907}}.

\bibitem{Solovjov_2000}
V.~P. Solovjov, B.~W. Webb, {SLW} modeling of radiative transfer in
  multicomponent gas mixtures, Journal of Quantitative Spectroscopy and
  Radiative Transfer 65 (2000) 655--672.

\bibitem{Solovjov_2001}
V.~P. Solovjov, B.~W. Webb, An efficient method for modeling radiative transfer
  in multicomponent gas mixtures with soot, Transactions of the ASME 123 (2001)
  450--457.

\bibitem{Solovjov_2008}
V.~P. Solovjov, B.~W. Webb, Multilayer modeling of radiative transfer by {SLW}
  and {CW} methods in non-isothermal gaseous medium, Journal of Quantitative
  Spectroscopy and Radiative Transfer 109~(2) (2008) 245--257.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2007.08.015}
  {\path{doi:10.1016/j.jqsrt.2007.08.015}}.

\bibitem{Solovjov_2011}
V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, The {SLW}-1 model for efficient
  prediction of radiative transfer in high temperature gases, Journal of
  Quantitative Spectroscopy and Radiative Transfer 112~(7) (2011) 1205--1212.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.08.009}
  {\path{doi:10.1016/j.jqsrt.2010.08.009}}.

\bibitem{Solovjov_2014}
V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, Extension of the exact {SLW} model to
  non-isothermal gaseous media, Journal of Quantitative Spectroscopy and
  Radiative Transfer 143 (2014) 83--91.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2013.10.008}
  {\path{doi:10.1016/j.jqsrt.2013.10.008}}.

\bibitem{Webb_2018}
B.~W. Webb, V.~P. Solovjov, F.~Andr{\'e}, An exploration of the influence of
  spectral model parameters on the accuracy of the rank correlated slw model,
  Journal of Quantitative Spectroscopy and Radiative Transfer 218 (2018)
  161--170.
\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2018.06.023}
  {\path{doi:10.1016/j.jqsrt.2018.06.023}}.

\bibitem{Pearson_2014}
J.~Pearson, B.~Webb, S.~V.P., J.~Ma, Efficient representation of the absorption
  line blackbody distribution function for {H$_2$O}, {CO$_2$}, and {CO} at
  variable temperature, mole fraction, and total pressure, Journal of
  Quantitative Spectrosopy and Radiative Transfer 138 (2014) 82--96.

\bibitem{Brewster_1992}
M.~Q. Brewster, Thermal Radiative Transfer and Properties, Wiley, 1992.

\bibitem{Lee_1981}
S.~C. Lee, C.~L. Tien, Optical constants of soot in hydrocarbon flames,
  Symposium (International) on Combustion 18~(1) (1981) 1159--1166.
\newblock \href {http://dx.doi.org/10.1016/S0082-0784(81)80120-8}
  {\path{doi:10.1016/S0082-0784(81)80120-8}}.

\bibitem{Stull_1960}
V.~R. Stull, G.~N. Plass, Emissivity of dispersed carbon particles, Journal of
  the Optical Society of America 50~(2) (1960) 121.
\newblock \href {http://dx.doi.org/10.1364/JOSA.50.000121}
  {\path{doi:10.1364/JOSA.50.000121}}.

\bibitem{Dalzell_1969}
W.~H. Dalzell, A.~F. Sarofim, Optical constants of soot and their application
  to heat-flux calculations, Journal of Heat Transfer 91~(1) (1969) 100--104.
\newblock \href {http://dx.doi.org/10.1115/1.3580063}
  {\path{doi:10.1115/1.3580063}}.

\bibitem{Howarth_1966}
C.~R. Howarth, P.~J. Foster, M.~W. Thring (Eds.), The Effect of Temperature on
  the Extinction of Radiation By Soot Particles, Begellhouse, 1966.
\newblock \href {http://dx.doi.org/10.1615/IHTC3.1210}
  {\path{doi:10.1615/IHTC3.1210}}.

\bibitem{Chang_1990}
H.-c. Chang, T.~T. Charalampopoulos, Determination of the wavelength dependence
  of refractive indices of flame soot, Proceedings of the Royal Society of
  London. Series A: Mathematical and Physical Sciences 430~(1880) (1990)
  577--591.
\newblock \href {http://dx.doi.org/10.1098/rspa.1990.0107}
  {\path{doi:10.1098/rspa.1990.0107}}.

\bibitem{Felske_1984}
J.~D. Felske, T.~T. Charalampopoulos, H.~S. Hura, Determination of the
  refractive indices of soot particles from the reflectivities of compressed
  soot pellets, Combustion Science and Technology 37~(5-6) (1984) 263--283.
\newblock \href {http://dx.doi.org/10.1080/00102208408923757}
  {\path{doi:10.1080/00102208408923757}}.

\bibitem{Williams_2007}
T.~C. Williams, C.~R. Shaddix, K.~A. Jensen, J.~M. Suo-Anttila, Measurement of
  the dimensionless extinction coefficient of soot within laminar diffusion
  flames, International Journal of Heat and Mass Transfer 50~(7-8) (2007)
  1616--1630.
\newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2006.08.024}
  {\path{doi:10.1016/j.ijheatmasstransfer.2006.08.024}}.

\bibitem{Felske_1977}
J.~Felske, T.~C.L., The use of the {M}ilne-{E}ddington absorption coefficient
  for radiative heat transfer in combustion systems, ASME Journal of Heat
  Transfer 99~(3) (1977) 633--647.

\bibitem{Bordbar_personal}
H.~Bordbar, personal communication.

\bibitem{Chang_1984}
S.~Chang, K.~Rhee, Blackbody radiation functions, International communictions
  in Heat and Mass Transfer 11 (1984) 451--455.

\bibitem{Stephens_2020}
V.~Stephens, D.~Lignell, One-dimensional turbulence ({ODT}): computationally
  efficient modeling and simulation of turbulent flows, Software{X} 13 (2020)
  100641.
\newblock \href {http://dx.doi.org/10.1016/j.softx.2020.100641}
  {\path{doi:10.1016/j.softx.2020.100641}}.

\end{thebibliography}
